---
title: "`amtGUI` User Report"
output: html_document
params:
  dataset: NA
  dataset_env: NA 
  epsg_csv: NA
  epsg_env: NA
  epsg_trk: NA
  x: NA
  y: NA
  ts: NA
  id: NA
  id_trk: NA 
  resamp_rate: NA
  tolerance: NA
  date_range: NA
  min_burst: NA
  env_cov: NA
  env_cat: NA
  tod: NA
  model: NA
  rand_stps: NA
  rand_points: NA
  mod_var: NA
  inter_no: NA
  inter_1: NA
  inter_2: NA
  inter_3: NA
  inter_4: NA
  inter_5: NA 

  
---
<br>
This user report serves as a simple way to reproduce the results of previous `amtGUI` sessions.  
You can save this file and reproduce your previous analysis using the input values below.

***

##### Uploaded dataset
```{r csv Input, echo=FALSE}
params$dataset
```

##### Uploaded environmental data
```{r environment, echo=FALSE}
params$dataset_env
```

##### EPSG code assigned in csv
```{r echo=FALSE}
params$epsg_csv
```

##### EPSG code assigned in map
```{r echo=FALSE}
params$epsg_env
```

##### EPSG code used in track creation
```{r echo=FALSE}
params$epsg_trk
```

##### User input for x-coordinates (longitude)
```{r echo=FALSE}
params$x
```

##### User input for y-coordinates (latitude)
```{r echo=FALSE}
params$y
```

##### User input for timestamp column
```{r echo=FALSE}
params$ts
```

##### User input for ID columb
```{r echo=FALSE}
params$id
```

##### User selected ID's for track creation
```{r echo=FALSE}
params$id_trk
```

##### Resampling rate
```{r echo=FALSE}
params$resamp_rate
```

##### Tolerance 
```{r echo=FALSE}
params$tolerance
```

##### Choosen date range 
```{r echo=FALSE}
params$date_range
```

##### Number of bursts set
```{r echo=FALSE}
params$min_burst
```

##### Environmental covariates converted into categorical?
```{r echo=FALSE}
params$env_cov
params$env_cat
```

##### Time of day included?
```{r echo=FALSE}
params$tod
```

##### Model type 
```{r echo=FALSE}
params$model
```

##### Number of random steps used (iSSF)
```{r echo=FALSE}
params$rand_stps
```

##### Number of random points used (RSF)
```{r echo=FALSE}
params$rand_points
```

##### Model covariates
```{r echo=FALSE}
params$mod_var
```

##### Number of interaction terms
```{r echo=FALSE}
params$inter_no
```

##### Interaction terms used
```{r echo=FALSE}
params$inter_1
params$inter_2
params$inter_3
params$inter_4
params$inter_5
```

